---
output:
  md_document:
    variant: markdown_github
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

berate : Provide Insightful Motivation During Interactive Sessions

No user exposed functions. Just add `library(berate)` to your `.Rprofile` or any interactive session to receive "helpful" motivations to code or type better.

### News

- Version 0.0.0.9999 released

### Installation

```{r eval=FALSE}
devtools::install_github("hrbrmstr/berate")
```

```{r echo=FALSE, message=FALSE, warning=FALSE, error=FALSE}
options(width=120)
```

### Usage

```{r}
library(berate)

# current verison
packageVersion("berate")

```

### Test Results

```{r}
library(berate)
library(testthat)

date()

test_dir("tests/")
```

### Code of Conduct

Please note that this project is released with a [Contributor Code of Conduct](CONDUCT.md). 
By participating in this project you agree to abide by its terms.
